---
title: "p8105_hw5_zo2168"
author: "Zhengkun Ou"
date: "2024-11-14"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(ggplot2)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

```{r}
birthday <- function(n){
  birthdays <- sample(1:365, n, replace = TRUE)
  any(duplicated(birthdays))
}

prob <- tibble(n = 2:50) %>%
  mutate(prob = map_dbl(n, ~mean(replicate(10000, birthday(.x)))))
prob

ggplot(prob, aes(x = n, y = prob)) +
  geom_line() +
  labs(title = "Probability of at least two people sharing a birthday",
       x = "Group size",
       y = "Probability")





```

##Question 2
```{r}
set.seed(123)

run_simulation <- function(mu, n = 30, sigma = 5, nsims = 5000) {
  results <- map_dfr(1:nsims, function(i) {
    x <- rnorm(n, mean = mu, sd = sigma)
    
    test_results <- t.test(x, mu = 0) %>% broom::tidy()
    
    list(
      sim = i,
      estimate = test_results$estimate,
      p_value = test_results$p.value
    )
  })
  
  results$true_mu <- mu
  results
}

mu_values <- c(0, 1, 2, 3, 4, 5, 6)
all_results <- map_dfr(mu_values, run_simulation)

summary_stats <- all_results %>%
  group_by(true_mu) %>%
  summarise(
    power = mean(p_value < 0.05),
    avg_estimate = mean(estimate),
    avg_estimate_rejected = mean(estimate[p_value < 0.05])
  )

```


```{r}
power_plot <- ggplot(summary_stats, aes(x = true_mu, y = power)) +
  geom_line() +
  geom_point() +
  labs(
    title = "Power Analysis for One-Sample T-Test",
    x = "True Value of μ",
    y = "Power (Proportion of Rejected Null Hypotheses)",
    caption = "Based on 5000 simulations per μ value\nn = 30, σ = 5, α = 0.05"
  )
power_plot
```
```{r}
estimates_plot <- ggplot(summary_stats, aes(x = true_mu)) +
  geom_line(aes(y = avg_estimate, color = "All Samples")) +
  geom_line(aes(y = avg_estimate_rejected, color = "Rejected Samples Only")) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", alpha = 0.5) +
  labs(
    title = "Average Estimates vs True μ",
    x = "True Value of μ",
    y = "Average Estimate",
    color = "Sample Type",
    caption = "Dashed line represents y = x"
  )
estimates_plot
```
### 1. Small Effect Sizes (μ ≈ 0-2)
* The yellow line (rejected samples) lies **above** the true value line (dashed y=x)
* This indicates an upward bias in the estimates when only considering significant results
* This phenomenon demonstrates selection bias or "winner's curse" - we're only seeing results extreme enough to reject the null hypothesis

### 2. Large Effect Sizes (μ > 4)
* The yellow line converges with:
    + The purple line (all samples)
    + The dashed line (true values)
* This convergence occurs because:
    + Larger effect sizes provide more statistical power
    + More tests reject the null hypothesis
    + Less selection bias as we're not just selecting extr

##Question 3
```{r}
suicide <- read_csv("homicide-data.csv")
suicide <- 
  suicide |>
  mutate(
    city_state = str_c(city, state, sep = ", ")
  ) |>
  filter(city_state != "Tulsa, AL") |>
  group_by(city_state) |>
  summarize(
    total_homicides = n(),
    unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
  )

run_prop_test <- function(n_unsolved, n_total) {
  prop.test(n_unsolved, n_total) |>
    broom::tidy() |>
    select(estimate, conf.low, conf.high)
}

baltimore_test <- suicide |>
  filter(city_state == "Baltimore, MD") |>
  summarize(
    result = run_prop_test(unsolved_homicides, total_homicides)
  )


city_proportions <- suicide |>
  mutate(
    test_results = map2(unsolved_homicides, total_homicides, \(x,y) run_prop_test(x, y)
    )
  ) |>
  unnest(test_results)

city_proportions
```

```{r}
ggplot(city_proportions, aes(x = fct_reorder(city_state, estimate))) +
  geom_point(aes(y = estimate)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(
    title = "Proportion of Unsolved Homicides by City",
    x = "City, State",
    y = "Proportion Unsolved",
  ) +
  theme(axis.text.x = element_text(size = 5, angle = 90))
```


